Median Maximum Pairwise Distance

### 2020-08-20 main.Rmd
size and power graphs added

@@

## Level and power

@@

### Scenario 1: Simulated same normal distributions for all combinations of categories for all harmony pairs.

@@

```{r samenull_2by4, eval = FALSE}

@@

*Conclusion*: The test does not select harmony pairs when distributions of categories are same

>>>>

```{r load_fun_1var}

```{r load_fun_2var}

@@

## Size and power

@@

### Size: Simulated same distribution for all combinations of categories for all harmony pairs.

@@

<!-- # ```{r samenull_2by4, eval = FALSE} -->
<!-- #  -->
<!-- # ``` -->

```{r normalv21_power}

@@

```{r normalv22_power}

### Power: Simulated same distribution for all combinations of categories for all harmony pairs.

```{r normalv23_power}

```{r normalv24_power}

*Conclusion*: The test does not select harmony pairs when distributions of categories are same.
